---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mixBag

<!-- badges: start -->
<!-- badges: end -->

*mixBag* is a package that encapsulates several repeated tasks that a data scientist performs regularly in data analysis and modeling into some simple wrapper functions. The main goals of *mixBag* are to make repeat activities faster and more efficient.

## Installation

This package is only available in GitHub. You can install the latest development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Curious-Joe/mixBag")
```
## Usage

*mixBag* has several useful functions aimed at simplifying tasks in different areas of work that a data analysis. Couple of examples are shown below:

### qtile_plot()

Plotting percentage of different target feature labels in different quantile groups of a predictor feature.

```{r example01}
library(mixBag)

# plot percentage of different target labels in different quartiles of a predictor
qtile_plot(iris,x_feat = Sepal.Length, y_feat = Species, quantile = 10)


```

### compare_classifiers()

Fit 5 classifiers on a training data and compare results based on ROC on provided test data. *mixBag* model related functions rely heavily upon the suite of packages that come along with *tidymodels* package.

```{r example02}
library(tidymodels)
library(rsample)
split <- initial_split(wine, strata = quality_bin)
train <- training(split)
test <- testing(split)
recipe <- recipe(quality_bin ~ ., data = train) %>%
  update_role(ID, new_role = 'identification') %>%
  step_string2factor(all_nominal()) %>%
  step_knnimpute(all_predictors()) %>%
  step_normalize(all_numeric())

compare_classifiers(recipe = recipe, test_df = test, target_lab = 1)
```

## Getting Help

For any question or bug fix feel free to send email at a.h.fahad90@gmail.com.


